Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-24 Draft.Rmd
dfgh

---
title: "Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S."
author: "Aileen Li, Nyah Strickland"
date: "2023-04-18"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

@@

```{r Library}
library(tidyverse)
library(tidymodels)
library(broom)
library(xgboost)
library(caret)
library(plotROC)
library(randomForest)
library(factoextra)
library(MASS)
library(ranger)
library(doParallel)

@@

## Results
### Predictor/Feature Extraction

@@

```{r LinearRegression}
set.seed(123)
# Fit model and get summary
fit_lm = lm(value ~ CMAQ+lat+county_area+lon+aod, data=train)
step <- stepAIC(fit_lm, direction="backward", trace=TRUE)
# Keeps cmaq and aod

>>>>

---
title: "Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S."
author: "Aileen Li, Nyah Strickland"
date: "2023-04-18"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```
## Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

@@

```{r Library message=FALSE}
library(tidyverse)
library(tidymodels)
library(broom)
library(xgboost)
library(caret)
library(plotROC)
library(randomForest)
library(factoextra)
library(MASS)
library(ranger)
library(doParallel)

@@

### Predictor/Feature Extraction

@@

```{r LinearRegression}
set.seed(123)
# Fit model and get summary
fit_lm = lm(value ~ CMAQ+lat+county_area+lon+aod, data=train)
step <- stepAIC(fit_lm, direction="backward", trace=FALSE)
# Keeps cmaq and aod
